Dissertation

### 2024-06-21 index.qmd
re-render
minor changes

>>>>

## Project 1

[{{< fa file-lines >}} Project 1 page](https://tegorman13.github.io/Dissertation/Sections/IGAS.html)

[{{< fa file-pdf >}} pdf of the journal
article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
[{{< fa scroll >}} Link to online version of journal
article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}

## Project 2

[{{< fa file-lines >}} Link to project 2 page](https://tegorman13.github.io/htw/){target="_blank"} \

[{{< fa file-pdf >}} Working Draft of Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
